{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-11-23 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, updated

\section{Preliminaries}\label{sec:preliminaries}
    Throughout the writing, let the ambient space is $\RR^n$. 
    The optimization problem is
    \begin{align*}
        \min_{x \in \RR^n} F(x). 
    \end{align*}
    This section introduces the Nesterov's estimating sequence technique. 
    This technique is fundamental for in Guler's accelerated PPM method and Catalyst meta acceleration in the convex/strongly convex case. 
    \subsection{Method of Nesterov's Estimating Sequence}
        \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
            Let $(\phi_k : \RR^n \rightarrow\RR)_{k \ge 0}$ be a sequence of functions. 
            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions: 
            \begin{enumerate}
                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k^*(x)$. 
                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ where $\alpha_k \in (0, 1)\; \forall k \ge0 $ such that for all $x \in \RR^n$ it has $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$. 
            \end{enumerate}
        \end{definition}
        \begin{observation} 
            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
            Then observe that $\forall k \ge 0$:  
            \begin{align*}
                \Delta_k(x) 
                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x)
                \\
                x = x_k\implies 
                \Delta_k(x_k) 
                &\ge 
                \phi_k^* - F(x_k) \ge 0
                \\
                x = x_* \implies 
                \Delta_k(x_*)
                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0
            \end{align*}
            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
            \begin{align*}
                \phi_{k + 1}(x) - \phi_k(x) 
                &\le - \alpha_k (\phi_k(x) - F(x))
                \\
                \iff 
                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
                &\le 
                -\alpha_k(\phi_k(x) - F(x))
                \\
                \iff
                \Delta_{k + 1}(x) - \Delta_k(x) &\le
                - \alpha_k\Delta_k(x)
                \\
                \iff 
                \Delta_{k + 1}(x) 
                &\le 
                (1 - \alpha_k)\Delta_k(x). 
            \end{align*}
            Unrolling the above recursion it yields: 
            \begin{align*}
                \Delta_{k + 1}(x) &\le 
                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
                \left(
                    \prod_{i = 0}^k(1 - \alpha_i)
                \right)\Delta_0(x). 
            \end{align*}
            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
            $$
                F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
            $$ 
        \end{observation}
        Creativity is important in the construction of the estimating sequence $(\phi_k)_{k \ge 0}$.

@@

\section{Guler 1993}
    This section introduces the setup of the Nesterov's estimating sequence used in Guler's accelerated Proximal Point method. 
    Guler showed Nesterov's estimating sequence technique can accelerate proximal point method from Rockafellar in the convex settings.

    Throughout this section, we assume that $F:\RR^n \rightarrow \overline \RR$ is a convex function. 
    We use the following list of notations: 
    \begin{align*}
        \mathcal M^{\lambda} (x; y) &:= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2
        \\
        \mathcal J_\lambda y &:= \argmin_x \mathcal M^{\lambda} (x; y)
        \\
        \mathcal G_\lambda &:= \lambda^{-1}(I - \mathcal J_\lambda). 
    \end{align*}
    For notations simplicity, we use $\mathcal G_k, \mathcal J_k$ to denote the gradient mapping and the proximal point operator because under the context of the algorithm, the proximal point step is conductive iteratively with some arbitrary sequence that $(\lambda)_{k \ge 0}$ which we fixed at the start.

@@

        The Nesterov's estimating sequence $(\phi_k)_{k \ge0}$ for the accelerated proximal point method is defined by the following recurrence for all $k \ge0$, any $A \ge 0$: 
            \phi_0 &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 

@@

        Then the descent sequence $x_k$, along with the auxiliary vector sequence $(y_k, v_k)$, scalar sequence $(\alpha_k, A_k)_{k\ge 0}$ will be made to satisfy for all $k\ge0$, the conditions: 

@@

            y_k &= (1 - \alpha_k)x_k + \alpha_k v_k

@@

            v_k - \frac{\alpha_k}{A_{k + 1}\lambda_k}(y_k - \mathcal J_k y_k)

@@

    To handle the inexact evaluation of the PPM, Guler cited Rockafellar \cite{rockafellar_monotone_1976} for condition (A') in his text which is the following: 

@@

    \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
        Let $F$ be a $\mu\ge 0$ strongly convex and fix $\kappa$. 
        If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$ it has for all $x$: 
        \begin{align*}
            F(x) &\ge 
            F(x_k) + \kappa \langle y_{k - 1} - x_k, x - x_k\rangle
            + \frac{\mu}{2}\Vert x - x_k\Vert^2 
            + (\kappa + \mu)\langle  x_k - x_k^*, x - x_k\rangle 
            - \epsilon_k.
        \end{align*}
    \end{lemma}
    \begin{remark}
        The lemma plays a key role because it allows Lin to denote his Nesterov's estimating sequence to be for all $k \ge0$: 
        \begin{align*}
            \phi_0 &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
            \\
            \phi_k(x) &:= 
            (1 - \alpha_{k - 1})\phi_{k - 1}(x)
            + \alpha_{k - 1}\left(
                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k \rangle
                + \frac{\mu}{2}\Vert x - x_k\Vert^2
            \right). 
        \end{align*}
        It is void of intractable quantities. 
    \end{remark}

@@

    \begin{theorem}[Basic 4WD Catalyst Convergence]\label{thm:basic-4wd-catalyst}
        Let $(x_k, v_k, y_k)$ be generated by the basic Catalyst algorithm. 
        If $F$ is $\kappa$ weakly convex and bounded below, then $x_k$ converges to stationarity where
        \begin{align*}
            \min_{j = 1, \cdots, N} \dist^2(\mathbf 0, \partial F(\bar x_j))
            \le \frac{8 \kappa}{N}(F(x_0) - F^*). 
        \end{align*}
        And when $F$ is convex, $F(x_k) - F^*$ converges at a rate of $\mathcal O(k^{-2})$. 
    \end{theorem}
    \begin{remark}
        Convergence to stationarity is strictly weaker than convergence to any stationarity point of $F$. 
        Read 
        \hyperref[app:sec:ncnvx-catalyst]{Section \ref*{app:sec:ncnvx-catalyst}} for more information on proof of this claim. 
    \end{remark}

@@

\appendix
\section{Theorems and claims for accelerated proximal gradient}\label{app:sec:thm-claim-acc-prox-grad}
    Throughout this section, $F = g + f$ is an additive composite objective function with $g$ convex, $f$ $L$-lipschitz smooth and $\mu \ge0$ strongly convex. 
    The notations here are 
    \begin{align*}
        \mathcal M^{L^{-1}}(x; y) 
        &:= 
        F(x) + \frac{L}{2}\Vert x - y\Vert^2
        \\
        \widetilde{ \mathcal M}^{L^{-1}}(x; y) 
        &:= g(x) + f(y) 
        + 
        \left\langle \nabla f(x), x - y\right\rangle 
        + 
        \frac{L}{2}\Vert x - y\Vert^2
        \\
        \widetilde{\mathcal J}_{L^{-1}}y 
        &:= \argmin_{x} \widetilde{\mathcal M}^{L^{-1}}(x; y)
        \\
        \widetilde{\mathcal G}_{L^{-1}}(y)
        &:= L\left(I - \widetilde{\mathcal J}_{L^{-1}}\right)y. 
    \end{align*}

@@

        Fix any $y$, we have for all $x \in \RR^n$: 

@@

        Next, since $\widetilde{\mathcal M}^{L^{-1}}(\cdot, y)$ is strongly convex, it has quadratic growth conditions on its minimizer. 
        Denote $y^+ = \widetilde{\mathcal J}_{L^{-1}}y$ then: 

@@

        Compare the same theorems in older literatures, this proof doesn't use the subgradient inequality, making it appealing for generalizations outside convexity context. 

@@

    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]\label{thm:canon-prox-grad-est-seq}
        \; \\
        Denote $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that it satisfies recursively for all $k\ge 0$ the following conditions 
        \begin{align*}
            & g_k := L(y_k - \widetilde{\mathcal J}_{L^{-1}} y_k)
            \\
            & l_F(x; y_k) := 
                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
                + \langle g_k, x - y_k\rangle 
                + \frac{1}{2L}\Vert g_k\Vert^2, 
            \\
            & \alpha_k \in (0, 1)
            \\
            & 
            \phi_{k + 1}(x)
            := (1 - \alpha_k)\phi_k (x) + 
            \alpha_k (l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2). 
        \end{align*}
        Where $(y_k)_{k\ge 0}$ is any auxiliary sequence. 
        If we define the canonical form for $\phi_k$ as convex quadratic parameterized by positive sequence $(\gamma_k), \phi_k^*$ and 
        \begin{align*}
            \phi_k^* := \min_{x} \phi_k(x)
            \\
            \phi_k(x) := \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2.
        \end{align*}
        Then the auxiliary sequence $y_k, v_k$, parameters for the canonical form of estimating sequence must satisfy for all $k\ge 0$ these inequalities: 
        {\small
        \begin{align*}      
            \gamma_{k + 1} &= (1 - \alpha_k) \gamma_k + \mu \alpha_k
            \\
            v_{k + 1} &= \gamma_{k + 1}^{-1}
            (\gamma_k(1 - \alpha_k)v_k - \alpha_k g_k + \mu \alpha_k y_k)
            \\
            \phi_{k + 1}^* &= 
            (1 - \alpha_k)\phi_k^*
            + \alpha_k\left(
                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
                + \frac{1}{2L}\Vert g_k\Vert^2 
            \right) 
            \\
            &\quad 
            - \frac{\alpha_k^2}{2 \gamma_{k + 1}} \Vert g_k\Vert^2 
            + 
            \frac{\alpha_k(1 - \alpha_k)\gamma_k}{\gamma_{k + 1}} 
            \left(
                \frac{\mu}{2}\Vert v_k - y_k\Vert^2 
                + \langle v_k - y_k , g_k\rangle
            \right). 
        \end{align*}
        }
    \end{theorem}

@@

        Because $v_{k + 1}$ is the minimizer of $\phi_{k+ 1}$ by definition of the canonical form, solving $\nabla \phi_{k + 1}(x) = \mathbf 0 $ yields $v_{k + 1}$. 
        This is obtained by considering the following: 

@@

            v_{k + 1} &:= x=

@@

        Substituting the canonical form of $\phi_{k + 1}$ back to \textcolor{red}{(eqn1)}, choose $x = y_k$, it gives the following: 

@@

        Next move from Nesterov was to simplify the term $\Vert v_{k + 1} - y_k\Vert^2$. 
        With that it produces: 

@@

                    &= - \gamma_{k + 1} + \mu \alpha_k

@@

        Next we have

@@

@@

        The second and third inequality used the equality $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \mu \alpha_k$. 
        The goal of having $\phi_k^*$ represented by iterates $v_k, y_k, g_k$ is because it assists in the future when an inductive hypothesis $\phi_k^* \ge F(x_k) \ge l_F(x_k; y_k) + \frac{\mu}{2}\Vert x - y_k\Vert^2$ is made. 
        We did things in advance here, nothing more. 

@@

@@

@@

        Now, recall from the fundamental proximal gradient inequality in the convex settings, we have $\forall z\in \RR^n$: 

@@

            & \text{set: }x_{k + 1} := \widetilde{\mathcal J}_{L^{-1}}y_k

@@

        Now we set $z = x_{k}$ and substitute it back to RHS of $\phi_{k + 1}$ which yields: 

@@

        To assert $\phi_{k + 1}^* \ge F(x_k)$, one set of sufficient conditions are 

@@

            \right) &\ge 0

@@

        Before we finish it, re-arranging should give use the equivalent representations 

@@

                \gamma_{k + 1} + \alpha_k \gamma_k 
                \gamma_k + \alpha_k \mu

@@

        And $\alpha_k, \gamma_k$, we have the equivalent representation of 

@@

            1 &\ge L \alpha_k^2 / \gamma_{k + 1}

@@

    \begin{definition}[Nesterov's accelerated proximal gradient raw form]
    \label{app:def:acc-prox-grad-raw-form}
        The accelerated proximal gradient algorithm generates vector iterates $x_k, y_k, v_k$ using auxiliary sequence $\alpha_k, \gamma_k$ such that for all $k\ge0$ they satisfy conditions: 
        \begin{align*}
            L\alpha_k^2 
            &\le 
            (1 - \alpha_k)\gamma_k + \alpha_k\mu = \gamma_{k + 1}; \alpha_k \in (0, 1), 
            \\
            y_k &= (\gamma_k + \alpha_k \mu)^{-1}
            (\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k),
            \\
            x_{k + 1}&= 
            \widetilde{\mathcal J}_{L^{-1}} y_k
            \\
            v_{k + 1} &= 
            \gamma_{k + 1}^{-1}
            \left(
                (1 - \alpha_k)\gamma_k v_k + \alpha_k \mu y_k - \alpha_k g_k
            \right). 
        \end{align*}
    \end{definition}

    \begin{theorem}[Intermediate form of accelerated proximal gradient]\label{app:theorem:acc-prox-grad-intermediate}\; \\
        Let iterates $(x_k, y_k, v_k)$ be given by the raw form of Nesterov's accelerated proximal gradient. 
        If we assume that $L\alpha_k^2 = \gamma_{k + 1}$, then it simplifies into the following representation without parameter $\gamma_k$: 
        \begin{align*}
            y_k &= 
            \left(
                1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
            \right)^{-1}
            \left(
                v_k + 
                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
            \right)
            \\
            x_{k + 1} &= 
            y_k - L^{-1}  g_k
            \\
            v_{k + 1} &= 
            \left(
                1 + \frac{\mu}{L \alpha_k - \mu}
            \right)^{-1}
            \left(
                v_k + 
                \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
            \right) - \frac{1}{L\alpha_{k}} g_k
            \\
            0 &= \alpha_k^2 - \left(\mu/L - \alpha_{k -1}^2\right) \alpha_k - \alpha_{k - 1}^2. 
        \end{align*}
        Here we have $g_k = \widetilde{\mathcal G}_{L^{-1}}y_k$. 
    \end{theorem}
    \begin{proof}

@@

            & \text{find } \alpha_{k + 1} \text{ such that: }L \alpha_{k + 1}^2 = (1 - \alpha_{k + 1})L \alpha_{k - 1} + \mu \alpha_{k + 1}
            & x_{k + 1} = \widetilde {\mathcal J}_{L^{-1}} y_k

@@

            \phi_0 &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 

@@

        In the canonical form, $v_{k + 1}$ is the minimizer of $\phi_{k + 1}$, it can be solved for by setting the gradient $\phi_{k + 1}(x)= \mathbf 0$ so for all $k\ge 0$: 

@@

                y_k = (1 - \alpha_k)x_k + \alpha_k v_k

@@

                &= 0

@@

                \gamma_{k + 1} &= (1 - \alpha_{k})\gamma_k + \alpha_k \mu = (\kappa + \mu)\alpha_{k - 1}^2

@@

>>>>

\section{Preliminaries}\label{sec:preliminaries}
    Throughout the writing, let the ambient space is $\RR^n$. 
    The optimization problem is
    \begin{align*}
        \min_{x \in \RR^n} F(x). 
    \end{align*}
    This section introduces the Nesterov's estimating sequence technique. 
    This technique is fundamental for in Guler's accelerated PPM method and Catalyst meta acceleration in the convex/strongly convex case. 
    Unlike proofs using a Lyapunov argument which requires knowing exactly the algorithm in advance to verify the convergence rate, Nesterov's estimating squence can produce an algorithm that generates iterates $(x_k)_{k \ge0}$ such that it converges at some rate. 
    \subsection{Nesterov's Estimating Sequence}
        \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
            Let $(\phi_k : \RR^n \rightarrow\RR)_{k \ge 0}$ be a sequence of functions. 
            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions: 
            \begin{enumerate}
                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k(x)$. 
                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ where $\alpha_k \in (0, 1)\; \forall k \ge0 $ such that for all $x \in \RR^n$ it has $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$. 
            \end{enumerate}
        \end{definition}
        \begin{observation} 
            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
            Then observe that $\forall k \ge 0$:  
            \begin{align*}
                \Delta_k(x) 
                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x)
                \\
                x = x_k\implies 
                \Delta_k(x_k) 
                &\ge 
                \phi_k^* - F(x_k) \ge 0
                \\
                x = x_* \implies 
                \Delta_k(x_*)
                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0
            \end{align*}
            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
            \begin{align*}
                \phi_{k + 1}(x) - \phi_k(x) 
                &\le - \alpha_k (\phi_k(x) - F(x))
                \\
                \iff 
                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
                &\le 
                -\alpha_k(\phi_k(x) - F(x))
                \\
                \iff
                \Delta_{k + 1}(x) - \Delta_k(x) &\le
                - \alpha_k\Delta_k(x)
                \\
                \iff 
                \Delta_{k + 1}(x) 
                &\le 
                (1 - \alpha_k)\Delta_k(x). 
            \end{align*}
            Unrolling the above recursion it yields: 
            \begin{align*}
                \Delta_{k + 1}(x) &\le 
                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
                \left(
                    \prod_{i = 0}^k(1 - \alpha_i)
                \right)\Delta_0(x). 
            \end{align*}
            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
            $$
                F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
            $$ 
        \end{observation}
        Creativity is important in the construction of the estimating sequence $(\phi_k)_{k \ge 0}$.

@@

\section{Guler's estimating sequence}
    This section introduces the setup of the estimating sequence in Guler's accelerated Proximal Point method \cite{guler_new_1992}. 
    Guler showed the technique can accelerate proximal point method in the convex settings. 
    Throughout the section, assume that $F:\RR^n \rightarrow \overline \RR$ is a convex function. 
    Define:
    \begin{align*}
        \mathcal M^{\lambda} (x; y) &:= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2, 
        \\
        \mathcal J_\lambda y &:= \argmin_x \mathcal M^{\lambda} (x; y), 
        \\
        \mathcal G_\lambda &:= \lambda^{-1}(I - \mathcal J_\lambda). 
    \end{align*}
    For simplicity, we use $\mathcal G_k, \mathcal J_k$ as short for $\mathcal G_{\lambda_k}, \mathcal J_{\lambda_k}$ where $(\lambda_k)_{k \ge 0}$ is a fixed sequence used in the proximal point on the $k$ iteration.

@@

        The estimating sequence  $(\phi_k)_{k \ge0}$ for the accelerated proximal point method is defined by the following recurrence for all $k \ge0$, any $A \ge 0$: 
            \phi_0(x) &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 

@@

        Then for all $k \ge 0$, the descent sequence $x_k$, along with the auxiliary vector sequence $(y_k, v_k)$, scalar sequence $(\alpha_k, A_k)_{k\ge 0}$ are generated by: 

@@

            \right), 
            y_k &= (1 - \alpha_k)x_k + \alpha_k v_k, 

@@

            v_k - \frac{\alpha_k}{A_{k + 1}\lambda_k}(y_k - \mathcal J_k y_k), 
            A_{k + 1} &= (1 - \alpha_k)A_k. 

@@

    For the inexact evaluation of PPM, Guler cited Rockafellar \cite{rockafellar_monotone_1976} for condition (A') in his text which is the following: 

@@

    \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
        Let $F$ be a $\mu\ge 0$ strongly convex and fix $\kappa$. 
        If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$, then it has for all $x$: 
        \begin{align*}
            F(x) &\ge 
            F(x_k) + \kappa \langle y_{k - 1} - x_k, x - x_k\rangle
            + \frac{\mu}{2}\Vert x - x_k\Vert^2 
            + (\kappa + \mu)\langle  x_k - x_k^*, x - x_k\rangle 
            - \epsilon_k.
        \end{align*}
    \end{lemma}
    \begin{remark}
        The lemma plays a key role because it allows Lin to denote his Nesterov's estimating sequence to be for all $k \ge0$: 
        \begin{align*}
            \phi_0(x) &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
            \\
            \phi_k(x) &:= 
            (1 - \alpha_{k - 1})\phi_{k - 1}(x)
            + \alpha_{k - 1}\left(
                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k \rangle
                + \frac{\mu}{2}\Vert x - x_k\Vert^2
            \right). 
        \end{align*}
        It is void of intractable quantities. 
    \end{remark}

@@

    \begin{theorem}[Basic 4WD Catalyst Convergence]\label{thm:basic-4wd-catalyst}
        Let $(x_k, v_k, y_k)$ be generated by the basic Catalyst algorithm. 
        If $F$ is $\kappa$ weakly convex and bounded below, then $x_k$ converges to stationary where
        \begin{align*}
            \min_{j = 1, \cdots, N} \dist^2(\mathbf 0, \partial F(\bar x_j))
            \le \frac{8 \kappa}{N}(F(x_0) - F^*). 
        \end{align*}
        And when $F$ is convex, $F(x_k) - F^*$ converges at a rate of $\mathcal O(k^{-2})$. 
    \end{theorem}
    \begin{remark}
        Convergence to stationary is strictly weaker than convergence to any stationary point of $F$. 
        Read 
        \hyperref[app:sec:ncnvx-catalyst]{Section \ref*{app:sec:ncnvx-catalyst}} for more information on proof of this claim. 
    \end{remark}

@@

\appendix
\section{Theorems and claims for accelerated proximal gradient}\label{app:sec:thm-claim-acc-prox-grad}
    Throughout this section, $F = g + f$ is an additive composite objective function with $g$ convex, $f$ $L$-lipschitz smooth and $\mu \ge0$ strongly convex. 
    The notations here are 
    \begin{align*}
        \mathcal M^{L^{-1}}(x; y),
        &:= 
        F(x) + \frac{L}{2}\Vert x - y\Vert^2,
        \\
        \widetilde{ \mathcal M}^{L^{-1}}(x; y) ,
        &:= g(x) + f(y) 
        + 
        \left\langle \nabla f(x), x - y\right\rangle 
        + 
        \frac{L}{2}\Vert x - y\Vert^2,
        \\
        \widetilde{\mathcal J}_{L^{-1}}y 
        &:= \argmin_{x} \widetilde{\mathcal M}^{L^{-1}}(x; y),
        \\
        \widetilde{\mathcal G}_{L^{-1}}(y)
        &:= L\left(I - \widetilde{\mathcal J}_{L^{-1}}\right)y. 
    \end{align*}

@@

        For any fixed $y$, we have for all $x \in \RR^n$: 

@@

        Next, since $\widetilde{\mathcal M}^{L^{-1}}(\cdot, y)$ is $L$-strongly convex, it has quadratic growth conditions on its minimizer $y^+$ where $y^+ := \widetilde{\mathcal J}_{L^{-1}}y$ so it implies:

@@

        Compare the same theorem in older literatures, this proof doesn't use the subgradient inequality, making it appealing for generalizations outside convexity. 

@@

    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]\label{thm:canon-prox-grad-est-seq}
        \; \\
        Denote $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that for all $k\ge 0$ it recursively satisfies the following conditions 
        \begin{align*}
            & g_k := L(y_k - \widetilde{\mathcal J}_{L^{-1}} y_k),
            \\
            & l_F(x; y_k) := 
                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
                + \langle g_k, x - y_k\rangle 
                + \frac{1}{2L}\Vert g_k\Vert^2, 
            \\
            & \alpha_k \in (0, 1),
            \\
            & 
            \phi_{k + 1}(x)
            := (1 - \alpha_k)\phi_k (x) + 
            \alpha_k (l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2), 
        \end{align*}
        where $(y_k)_{k\ge 0}$ any sequence. 
        If we define the canonical form for $\phi_k$ as convex quadratic parameterized by positive sequence $(\gamma_k), \phi_k^*$:  
        \begin{align*}
            \phi_k(x) &:= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2, 
        \end{align*}
        where $\phi_k^* := \min_{x} \phi_k(x)$. 
        Then the auxiliary sequence $y_k, v_k$, parameters for the canonical form of estimating sequence must satisfy for all $k\ge 0$: 
        {\small
        \begin{align*}      
            \gamma_{k + 1} &= (1 - \alpha_k) \gamma_k + \mu \alpha_k,
            \\
            v_{k + 1} &= \gamma_{k + 1}^{-1}
            (\gamma_k(1 - \alpha_k)v_k - \alpha_k g_k + \mu \alpha_k y_k),
            \\
            \phi_{k + 1}^* &= 
            (1 - \alpha_k)\phi_k^*
            + \alpha_k\left(
                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
                + \frac{1}{2L}\Vert g_k\Vert^2 
            \right) 
            \\
                &\quad 
                - \frac{\alpha_k^2}{2 \gamma_{k + 1}} \Vert g_k\Vert^2 
                + 
                \frac{\alpha_k(1 - \alpha_k)\gamma_k}{\gamma_{k + 1}} 
                \left(
                    \frac{\mu}{2}\Vert v_k - y_k\Vert^2 
                    + \langle v_k - y_k , g_k\rangle
                \right). 
        \end{align*}
        }
    \end{theorem}

@@

        Because $v_{k + 1}$ is the minimizer of $\phi_{k+ 1}$ by definition of the canonical form, solving for $x$ in $\nabla \phi_{k + 1}(x) = \mathbf 0$ yields $v_{k + 1}$ by: 

@@

            v_{k + 1} := x&=

@@

        Substituting the canonical form of $\phi_{k + 1}$ back to \textcolor{red}{(eqn1)}, choose $x = y_k$, it gives: 

@@

        Next, we simplify $\Vert v_{k + 1} - y_k\Vert^2$ to get rid of $v_{k + 1}$. 

@@

@@

        From the second to third inequality, we used: 
                &= - \gamma_{k + 1} + \mu \alpha_k. 
        Therefore, it has: 

@@

        From the second to third equality we added and then transformed the coefficient of $\Vert y_k - v_k\Vert$ using: 

@@

        From the second to the third line, $\mu \alpha_k$ is brought in by the equation $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \mu \alpha_k$.

    \end{proof}
    \begin{remark}
        The goal of having $\phi_k^*$ represented by iterates $v_k, y_k, g_k$ is because it assists in the future when an inductive hypothesis $\phi_k^* \ge F(x_k) \ge l_F(x_k; y_k) + \frac{\mu}{2}\Vert x - y_k\Vert^2$ is made. 
        We did things in advance here and grouped together a set of transforms by equations, nothing more. 
    \end{remark}

@@

            \begin{split}

@@

            \end{split}
            \label{app:acc-prox-grad-ineq1}
        \end{align}

@@

        Now, recall from the fundamental proximal gradient inequality in the convex setting; define $x_{k + 1} := \widetilde{\mathcal J}_{L^{-1}}y_k$, we have $\forall z\in \RR^n$: 

@@

@@

        Next, set $z = x_{k}$ and substitute it back to RHS of $\phi_{k + 1}^*$ in 
        \hyperref[app:acc-prox-grad-ineq1]{Inequality \ref*{app:acc-prox-grad-ineq1}}: 

@@

        To assert $\phi_{k + 1}^* \ge F(x_{k + 1})$, one set of sufficient conditions are 

@@

            \right) &\ge 0, 

@@

        Before finishing, re-arranging should give use the equivalent representations 

@@

@@

        On the second to third equality, we multiplied the numerator and denominator by $\gamma_{k + 1}$ and then simplified the numerator using equation $\gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$. 
        For $\alpha_k, \gamma_k$, we have the equivalent representation of 

@@

            \iff 1 &\ge L \alpha_k^2 / \gamma_{k + 1}

@@

    \begin{definition}[Nesterov's accelerated proximal gradient raw form]
    \label{app:def:acc-prox-grad-raw-form}
        The accelerated proximal gradient algorithm generates vector iterates $x_k, y_k, v_k$ using auxiliary sequence $\alpha_k, \gamma_k$ such that for all $k\ge0$ they satisfy conditions: 
            (1 - \alpha_k)\gamma_k + \alpha_k\mu = \gamma_{k + 1}; \alpha_k \in (0, 1), 
            (\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k),
            x_{k + 1}&= 
            \widetilde{\mathcal J}_{L^{-1}} y_k
                (1 - \alpha_k)\gamma_k v_k + \alpha_k \mu y_k - \alpha_k g_k
    \begin{theorem}[Intermediate form of accelerated proximal gradient]\label{app:theorem:acc-prox-grad-intermediate}\; \\
        Let iterates $(x_k, y_k, v_k)$ be given by the raw form of Nesterov's accelerated proximal gradient which is 
        \hyperref[app:def:acc-prox-grad-raw-form]{Definition \ref*{app:def:acc-prox-grad-raw-form}}. 
        Assume for all $k \ge 0$ it has $L\alpha_k^2 = \gamma_{k + 1}$, then Definition \ref*{app:def:acc-prox-grad-raw-form} is algebraically equivalent to the following form which doesn't have $\gamma_k$: 
            x_{k + 1} &= 
            y_k - L^{-1}  g_k
                1 + \frac{\mu}{L \alpha_k - \mu}
                \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
            \right) - \frac{1}{L\alpha_{k}} g_k
            0 &= \alpha_k^2 - \left(\mu/L - \alpha_{k -1}^2\right) \alpha_k - \alpha_{k - 1}^2. 
        Here we have $g_k = \widetilde{\mathcal G}_{L^{-1}}y_k$. 

@@

            & \text{find } \alpha_{k + 1} \text{ such that: }L \alpha_{k + 1}^2 = (1 - \alpha_{k + 1})L \alpha_{k - 1} + \mu \alpha_{k + 1}, 
            & x_{k + 1} = \widetilde {\mathcal J}_{L^{-1}} y_k, 

@@

            \phi_0(x) &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 

@@

        In the canonical form, $v_{k + 1}$ is the minimizer of $\phi_{k + 1}$, it can be solved for by setting the gradient $\phi_{k + 1}(v_{k + 1})= \mathbf 0$ so for all $k\ge 0$: 

@@

                y_k = (1 - \alpha_k)x_k + \alpha_k v_k, 

@@

                &= 0, 

@@

                \gamma_{k + 1} &= (1 - \alpha_{k})\gamma_k + \alpha_k \mu = (\kappa + \mu)\alpha_{k - 1}^2,

@@

                (\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k),
